A Bradley-Terry analysis of three grandmasters: Karpov, Kasparov, Anand

### 2024-10-18 inst/carcinoma.Rmd
consistentify "time to process" information

To cite the `hyper2` package in publications, please use @hankin2017
(takes maybe twenty minutes to run without cache.  The value of
`carcinoma_maxp` is calculated separately [discussed below], and that
takes a few days to run).

This is a short analysis of the carcinoma dataset presented by
Agresti, table 13.1, p542.  Seven pathologists classified each of 118
slides on the presence or absence of carcinoma in the uterine cervix.

>>>>

<font size="1"> (takes about fifteen minutes to run without cache; the
value of `carcinoma_maxp` is calculated separately [discussed below],
and that takes a few days to run.  </font>

To cite the `hyper2` package in publications, please use
@hankin2017_rmd.  This is a short analysis of the carcinoma dataset
presented by Agresti, table 13.1, p542.  Seven pathologists classified
each of 118 slides on the presence or absence of carcinoma in the
uterine cervix.

### 2024-10-18 inst/global_liveability_ranking.Rmd
consistentify "time to process" information

To cite the `hyper2` package in publications, please use @hankin2017_rmd;
takes about an hour to process without cache.

_This analysis is essentially without value, see the very end for why_

[The global liveability
ranking](https://en.wikipedia.org/wiki/Global_Liveability_Ranking)
shows the nicest places to live.

>>>>

<font size="1"> (takes about an hour to run without cache)
</font>

*This analysis is essentially without value, see the
very end for why*

To cite the `hyper2` package in publications, please use
@hankin2017_rmd.  [The global liveability
ranking](https://en.wikipedia.org/wiki/Global_Liveability_Ranking)
shows the nicest places to live.

### 2024-10-18 inst/kka.Rmd
clarification that white_draw3() is a package function
consistentify "time to process" information

To cite the `hyper2` package in publications, please use @hankin2017_rmd;
this `Rmd` file takes about 45 minutes to process without cache.  Here
we define dataset `kka` which is the observed scorelines between
players Karpov, Kasparov, and Anand.  It is used to calculate
likelihood functions: `karpov_kasparov_anand`, `kka_3whites` and
`kka_3draws`.  This Rmd file supercedes files
`inst/karpov_kasparov_anand.R` and `inst/kka_3draws.R` and
`inst/kka_array.R`.  Some more detail is given in `man/kka.Rd`.

@@

We can use the bespoke function `white_draw3()` to make a likelihood
function:

>>>>

<font size="1"> (takes about forty five minutes to run without cache)
</font>

To cite the `hyper2` package in publications, please use
@hankin2017_rmd.  Here we define dataset `kka` which is the observed
scorelines between players Karpov, Kasparov, and Anand.  It is used to
calculate likelihood functions: `karpov_kasparov_anand`, `kka_3whites`
and `kka_3draws`.  This Rmd file supercedes files
`inst/karpov_kasparov_anand.R` and `inst/kka_3draws.R` and
`inst/kka_array.R`.  Some more detail is given in `man/kka.Rd`.

@@

We can use the bespoke function `hyper2::white_draw3()` to make a
likelihood function:
